
\documentclass[11pt,a4paper,roman]{moderncv}
% modern themes
\moderncvstyle{banking}                            
\moderncvcolor{blue}                               
\nopagenumbers{}                                  

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{comment}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{multicol}

\usepackage{import}

% personal data
\name{Cao Jilin}{}

\address{2315 Bowditch Street, Berkeley, CA 94706 }{}{}

  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

\begin{document}

\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
 \faGlobe\enspace caojilin.net & \faEnvelopeO\enspace caojilin@berkeley.edu & \faGithub\enspace caojilin &  \faMobile\enspace 510-646-3844\\  
\end{tabular}
\end{center}

\section{EDUCATION}
{\customcventry{May 2019}{Bachelor of Arts in Statistics}{University of California, Berkeley}{Berkeley, CA}{}{}}
\section{Key Skills}
Programming Languages: Python, R, Java, P5

\section{Related Coursework}
Deep Learning, Linear Programming and Network Flow, Linear Modeling, Machine Learning, Algorithms, Data Structure, Probability, Linear Algebra

\section{ACADEMIC PROJECTS}
%https://github.com/caojilin
{\customcvproject{Boston Housing | R}{Sep 2018 - Nov 2018}
  {\begin{itemize}
    \item A systematic data analysis using linear model. Predicting the Value of a Boston Home Using Neighborhood Features.
Started by doing EDA, then performing diagnostics: used various model selection techniques such as AIC, BIC,
Cross-Validation etc. and removed outliers to improve the model.
  \end{itemize}
  }
}

{\customcvproject{Digits classification and Language Identification | Python}{Feb 2018 – May 2018}
{\begin{itemize}
  \item Implemented neural network models, using gradient descent to optimize loss function and other techniques to improve the
model performance.
\end{itemize}
}

{\customcvproject{BearMaps | Java}{Jan 2018 – May 2018}
{\begin{itemize}
  \item Programmed the back-end of a web mapping application of Berkeley, CA that supported features such as image rastering at
different zoom levels, autocomplete location search, and route mapping
\end{itemize}
}
}


\section{EXPERIENCE}

{\customcventry{June 2017 - July 2017}{State Grid Corporation}{Data Analyst Intern}{HangZhou, China}{}
{\begin{itemize}
  \item Analyzed how the power usage distributed in different areas in a city and how the price of electricity relates to the
population of the city and other factors. Helped company to decide the location of installing new equipment. Presented a
visualization report to the company manager
\end{itemize}
}
}

{\customcventry{Sep 2018 - Now}{}{Lab Assistant for CS 61B}{Berkeley, CA}{}
{\begin{itemize}
  \item Every week, I helped students understand the material covered in class and helped them work through their weekly labs
and also worked at Office Hours.
\end{itemize}
}
}
{\customcventry{Sep 2018 - Now}{}{Lab Assistant for Stat 133}{Berkeley, CA}{}
{\begin{itemize}
  \item I helped students in a lab with 30 students weekly and teach them how to use R to do data analysis
\end{itemize}
}
}

\section{AWARDS AND ACHIEVEMENTS}
\begin{minipage}{\maincolumnwidth}%
	\small{
    	\begin{itemize}
          \item 2018 Cal DataFest Team of Best Visualization
          \item Fluent in Chinese
		\end{itemize}}%
\end{minipage}%
}

\end{document}


%% end of file `template.tex'.
