\documentclass{tccv}
\usepackage[english]{babel}

\begin{document}





\part{Rachel Karen Green}

\section{Work experience}

\begin{eventlist}

\item{July 2007 -- Present}
     {Gucci, NYC}
     {Director of Fashion Product Development}

Used communication sills to build strong relationships with retailers, both brick and mortar and online, and to expand and diversify the product presence with retailers. 

Product development — everything from ideating new products, dealing with manufacturers, managing packaging development, managing designers, writing copy, etc. The ideal candidate would have exposure to all of these areas and be confident spearheading these efforts.

\item{January 2002 -- June 2004}
     {Ralph Lauren, NYC}
     {Executive of Little Boy Clothing Department}

Had a firm understanding of the economics of wholesaling consumer products with high understanding of what specific retailers expect for margins and how to negotiate on these terms. 

Used strong sense for corporate finance — specifically as it pertains to budgeting, forecasting, opportunity analysis, etc.


\item{October 1998 -- November 2001}
     {Bloomingdales, NYC}
     {Fashion Developer}

Responsible for planning, developing and presenting fashion-focused products for a specific market of the fashion.

Worked closely with the design and technical team, and involved in developing seasonal collections from design concept through to prototypes. Also involved in trips overseas to source new fashion trends, ideas and concepts whether it is for womenswear, menswear, childrenswear, fashion accessories, footwear, or lingerie.


\item{September 1996 -- September 1998}
     {Central Perk Coffee, NYU}
     {Waitress}

Being responsible for taking food & drink orders from tables in the assigned section.

Assisted housemen in setting up buffets & food stations for dinners & events.

Conduct wine & coffee service in proper fashion.


\end{eventlist}

\personal
    [www.rachelgreen.com]
    {520 Mission St., NYC}
    {+1 510-816-xxxx}
    {pretty-rachel@gmail.com}

\section{Education}

\begin{yearlist}

\item[High school diploma]{1988 -- 1992}
     {Cheerleader}
     {Jungle Tree High School, NYC}

\item{1987 -- 1988}
     {Cheerleader}
     {Friends University, NYC}

\end{yearlist}

\section{Best Friends}

\begin{yearlist}

\item{1}
     {Monica (Oldest Friend)}
     {Known each other since high school}

\item{2}
     {Ross (Old Boyfriend)}
     {Monica's Brother}

\item{3}
     {Joey (Cutest Friend)}
     {Monica's Neighbor}

\item{4}
     {phoebe (Weirdest Friend)}
     {Monica's Old Roommate}

\item{5}
     {Chandler ("Funniest" Friend)}
     {Joey's Roommate}
     
\item{6}
     {Mindy (Ex- best friend)}
     

\end{yearlist}

\section{Skills}

\begin{factlist}
\item{English}{Native Speaker}
\item{Sailing}{High-level}
\item{Good Taste}{Very good at choosing clothing}
\item{Office}{Proficient in Words, Excel and Powerpoint}
\end{factlist}

\section{Hobbies}

\begin{factlist}

\item{Highest level}
     {Shopping, Doing makeups, Being cute, Reading fashion magazines}

\item{Intermediate}
     {Travelling, Driving, Dealing with her Relationship}

\item{Basic level}
     {Study, Reading, Cooking}

\end{factlist}

\end{document}
